Distinguish Real and Fake UHD Images with Relative Discrete Cosine Transform (RDCT)

### 2019-12-23 3-UHD/report/paper.tex
fix report layout

\subsubsection{Bilinear Interpolation}
\par First do linear interpolation in the x-direction:
\begin{align*}
p(R_1) = \frac{x_2-x}{x_2-x_1}\cdot p(Q_{11})+\frac{x-x_1}{x_2-x_1}\cdot p(Q_{21})\\
p(R_2) = \frac{x_2-x}{x_2-x_1}\cdot p(Q_{12})+\frac{x-x_1}{x_2-x_1}\cdot p(Q_{22})
\end{align*}
Then interpolate in the y-direction:
\begin{align*}
p(P) &= \frac{y2-y}{y2-y1}\cdot p(R_1)+\frac{y-y1}{y2-y1}\cdot p(R_2)\\ &=\small{\frac {1}{(x_{2}-x_{1})(y_{2}-y_{1})}} F {\begin{bmatrix}y_{2}-y\\y-y_{1}\end{bmatrix}} \\
& \text{where } F = {\begin{bmatrix}x_{2}-x&x-x_{1}\end{bmatrix}}{\begin{bmatrix}f(Q_{11})&f(Q_{12})\\f(Q_{21})&f(Q_{22})\end{bmatrix}}
\end{align*}
\par We can get the corresponding pixel's coordinate in original image: $x'\cdot scale\_x=x$, $y'\cdot scale\_y=y$. If either x or y is not integer, $x_1=int(x),x_2=int(x)+1,y_1=int(y), y_2=int(y)+1$, do interpolation.
\par This algorithm reduces some of the visual distortion caused by resizing an image to a non-integral zoom factor.
~\\
\subsubsection{Bicubic Interpolation}
~\\
\par In this method, new image’s pixel at point (x', y'), p(x',y'), is the weighted average of the nearest 16 points in the original image. An interpolator can be obtained by applying a convolution with the following kernel in both dimensions:
\begin{align*}
{\displaystyle W(x)={\begin{cases}(a+2)|x|^{3}-(a+3)|x|^{2}+1&{\text{for }}|x|\leq 1,\\a|x|^{3}-5a|x|^{2}+8a|x|-4a&{\text{for }}1<|x|<2,\\0&{\text{otherwise}},\end{cases}}}
\end{align*}
where a is usually set to $-0.5$ or $-0.75$.
\par $x'\cdot scale\_x=x$, $y'\cdot scale\_y=y$. If either x or y is not integer, $x_i$=int(x+i), $y_j$=int(y+j), i, j = -1,0,1,2:

do interpolation in the x-direction:
\begin{align*}
p(x',y_j)=\sum_{i}{W(x-x_i)\cdot p(x_i,y_j)}
\end{align*}
then do interpolation in the y-direction:
\begin{align*}
p(x',y')=\sum_{j}{W(y-y_j)\cdot p(x',y_j)} 
\end{align*}
\par Images resampled with bicubic interpolation are smoother and have fewer interpolation artifacts.
~\\
\subsubsection{Lanczos Resampling}
~\\
\par The effect of each input sample on the interpolated values is defined by the filter's reconstruction kernel L(x), called the Lanczos kernel. 
\begin{align*}
{\displaystyle L(x)={\begin{cases}\operatorname {sinc} (x)\,\operatorname {sinc} (x/a)&{\text{if}}\ -a<x<a,\\0&{\text{otherwise}}.\end{cases}}}
\end{align*}
Equivalently,
\begin{align*}
{\displaystyle L(x)={\begin{cases}1&{\text{if}}\ x=0,\\{\dfrac {a\sin(\pi x)\sin(\pi x/a)}{\pi ^{2}x^{2}}}&{\text{if}}\ -a\leq x<a\ {\text{and}}\ x\neq 0,\\0&{\text{otherwise}}.\end{cases}}}
\end{align*}
\par The parameter $a$ is a positive integer, typically 2 or 3 (but in opencv, the method is cv2.INTER$\_$LANCZOS4, $a$=4), which determines the size of the kernel. The Lanczos kernel has $2a-1$ labes:a positive one at the center, and $a-1$ alternating negative and positive lobes on each side.
\begin{align*}
L(x,y) &= L(x) \cdot L(y)\\
p(x',y') &= \sum_{i,j}{L(x_i-x)\cdot L(y_j-y)\cdot p(x_i,y_j)}
\end{align*}
$x_i=int(x+i)$, $y_j=int(y+j)$, $-a+1\leq i, j \leq a-1$

>>>>

\subsubsection{Bilinear Interpolation}
\par First do linear interpolation in the x-direction:
\begin{align*}
p(R_1) = \frac{x_2-x}{x_2-x_1}\cdot p(Q_{11})+\frac{x-x_1}{x_2-x_1}\cdot p(Q_{21})\\
p(R_2) = \frac{x_2-x}{x_2-x_1}\cdot p(Q_{12})+\frac{x-x_1}{x_2-x_1}\cdot p(Q_{22})
\end{align*}
Then interpolate in the y-direction:
\begin{align*}
p(P) &= \frac{y2-y}{y2-y1}\cdot p(R_1)+\frac{y-y1}{y2-y1}\cdot p(R_2)\\ &=\small{\frac {1}{(x_{2}-x_{1})(y_{2}-y_{1})}} F {\begin{bmatrix}y_{2}-y\\y-y_{1}\end{bmatrix}} \\
\end{align*}
\begin{align*}
\text{where } F = {\begin{bmatrix}x_{2}-x&x-x_{1}\end{bmatrix}}{\begin{bmatrix}f(Q_{11})&f(Q_{12})\\f(Q_{21})&f(Q_{22})\end{bmatrix}}
\end{align*}
\par We can get the corresponding pixel's coordinate in original image: $x'\cdot scale\_x=x$, $y'\cdot scale\_y=y$. If either x or y is not integer, $x_1=int(x),x_2=int(x)+1,y_1=int(y), y_2=int(y)+1$, do interpolation.
\par This algorithm reduces some of the visual distortion caused by resizing an image to a non-integral zoom factor.

\subsubsection{Bicubic Interpolation}
In this method, new image’s pixel at point (x', y'), p(x',y'), is the weighted average of the nearest 16 points in the original image. An interpolator can be obtained by applying a convolution with the following kernel in both dimensions:
\begin{align*}
{\displaystyle W(x)={\begin{cases}(a+2)|x|^{3}-(a+3)|x|^{2}+1&{\text{for }}|x|\leq 1,\\a|x|^{3}-5a|x|^{2}+8a|x|-4a&{\text{for }}1<|x|<2,\\0&{\text{otherwise}},\end{cases}}}
\end{align*}
where a is usually set to $-0.5$ or $-0.75$.
\par $x'\cdot scale\_x=x$, $y'\cdot scale\_y=y$. If either x or y is not integer, $x_i$=int(x+i), $y_j$=int(y+j), i, j = -1,0,1,2:

do interpolation in the x-direction:
\begin{align*}
p(x',y_j)=\sum_{i}{W(x-x_i)\cdot p(x_i,y_j)}
\end{align*}
then do interpolation in the y-direction:
\begin{align*}
p(x',y')=\sum_{j}{W(y-y_j)\cdot p(x',y_j)} 
\end{align*}

Images resampled with bicubic interpolation are smoother and have fewer interpolation artifacts.

\subsubsection{Lanczos Resampling}
The effect of each input sample on the interpolated values is defined by the filter's reconstruction kernel L(x), called the Lanczos kernel. 
% \begin{align*}
% {\displaystyle L(x)={\begin{cases}\operatorname {sinc} (x)\,\operatorname {sinc} (x/a)&{\text{if}}\ -a<x<a,\\0&{\text{otherwise}}.\end{cases}}}
% \end{align*}
% Equivalently,
\begin{align*}
{\displaystyle L(x)={\begin{cases}1&{\text{if}}\ x=0,\\{\dfrac {a\sin(\pi x)\sin(\pi x/a)}{\pi ^{2}x^{2}}}&{\text{if}}\ -a\leq x<a\ {\text{and}}\ x\neq 0,\\0&{\text{otherwise}}.\end{cases}}}
\end{align*}
\par The parameter $a$ is a positive integer, typically 2 or 3 (but in opencv, the method is cv2.INTER$\_$LANCZOS4, $a$=4), which determines the size of the kernel. The Lanczos kernel has $2a-1$ labes:a positive one at the center, and $a-1$ alternating negative and positive lobes on each side.
\begin{align*}
L(x,y) &= L(x) \cdot L(y)\\
p(x',y') &= \sum_{i,j}{L(x_i-x)\cdot L(y_j-y)\cdot p(x_i,y_j)}
\end{align*}
$x_i=int(x+i)$, $y_j=int(y+j)$, $-a+1\leq i, j \leq a-1$
